---
title: "CLT"
author: "Alexis Velasco"
date: '2022-06-08'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(lattice)
```

```{r}
Homers_data <- read.csv(file="Homers_data.csv")
my1000 <- sample(Homers_data$kkardashtemp ,size = 1000, replace=T)
densityplot(my1000,main="original data")
orignalmean<- mean(my1000)
orignalSD<-sd(my1000) 
```

Describe the resulting plot -  is it unimodal?  How many peaks does it have?  Are all the peaks the same size? 

The plot is not unimodel because it shows two peaks. One on the side where it shows people dislike Kim Kardashian
the other a little taller on the side that loves her. The mean of the data is `r orignalmean` and the standard deviation is `r orignalSD`. 


Now take 2 random samples of 1000 points of the kkardashtemp variable and form 1000 points of their averages,
 
```{r}
numb = 2
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 2")
samplemean<- mean(x.avg)
sampleSD<-sd(x.avg)
```

The plot is not unimodel because it shows three peaks. the tallest begins in the middle those who are okay with her the next would be those that love her and the last peak and the smallest are those who hate her. The mean for the peaks would be `r samplemean` and the standard deviation would be `r sampleSD`.
 
 ```{r}
numb = 4
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 4")
sample4mean<- mean(x.avg)
sample4SD<-sd(x.avg)
```
 Sample size 4 is not unimodel with 4 different peaks the hight sitting in the middle and the lowest toward the end by the x.avg 80-100.The mean for the peaks would be `r sample4mean` and the standard deviation would be `r sample4SD`. 

```{r}
numb = 9
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 9")
sample9mean<- mean(x.avg)
sample9SD<-sd(x.avg)
```

Sample size 9 is not unimodel by having multiple peaks through out the chart.By observing the peaks it seems many people's opinion sit in between hating her and liking her.The mean for the peaks would be `r sample9mean` and the standard deviation would be `r sample9SD`. 

```{r}
numb = 16
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 16")
sample16mean<- mean(x.avg)
sample16SD<-sd(x.avg)
```
The mean for the peaks would be `r sample16mean` and the standard deviation would be `r sample16SD`. 

```{r}
numb = 36
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 36")
sample36mean<- mean(x.avg)
sample36SD<-sd(x.avg)
```
The mean for the peaks would be `r sample36mean` and the standard deviation would be `r sample36SD`. 


Write a summary paragraph describing what you observed and how it relates to the central limit theorem.

When there is a small sample size the graphs are clearly not unimodel by having multiple and different peaks through out the graph. However when the sample size grows the amount of peaks shrink but still has a difference in it that create peaks, until the sample size is 36 where it often but not always shows unimodel. The data shows most people have a mediocre opinion of Kim Kardashian. The only time we see those who definitely hate her and love her are when the sample size are small. It can be seen in the mean of the samples having a mean around 50 which is the exact middle of the possible rating to 100.


