---
title: "CLT"
author: "Alexis Velasco"
date: '2022-06-08'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(lattice)
```

```{r}
Homers_data <- read.csv(file="Homers_data.csv")
my1000 <- sample(Homers_data$kkardashtemp ,size = 1000, replace=T)
densityplot(my1000,main="original data")
orignalmean<- mean(my1000)
orignalSD<-sd(my1000) 
```

Describe the resulting plot -  is it unimodal?  How many peaks does it have?  Are all the peaks the same size? 

The plot is not unimodel because it shows two peaks. One on the side where it shows people dislike Kim Kardashian
the other a little taller on the side that loves her. The mean of the data is `r orignalmean` and the standard deviation is `r orignalSD`. 


Now take 2 random samples of 1000 points of the kkardashtemp variable and form 1000 points of their averages,
 
```{r}
numb = 2
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 2")
samplemean<- mean(x.avg)
sampleSD<-sd(x.avg)
```

The plot is not unimodel because it shows three peaks. the tallest begins in the middle those who are okay with her the next would be those that love her and the last peak and the smallest are those who hate her. The mean for the peaks would be `r samplemean` and the standard deviation would be `r sampleSD`.
 